Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-11 WSSSPE4_report/WSSSPE4_paper.tex
shortening another wg section

\input{wg_alliance}
\input{wg_prototyping}
\input{wg_codemeta}
\input{wg_best_practices_developing}
\input{wg_social}
\input{wg_best_practices_undergrads}
\input{wg_metrics}
\input{wg_access}
\input{wg_soft_eng}
\input{wg_open_research_index}
\input{wg_letters}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Software Sustainability Alliance}
\label{sec:alliance}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\note{Neil and Jean wrote this}

The Software Sustainability Alliance working group aims to establish an alliance between organizations interested in improving the sustainability of research software. Such an alliance would ease the collaboration between member organizations to improve the sharing of expertise, resources and best practices. 
These organizations are funded groups or teams that aim to advance research software sustainability beyond their local university or community. More specifically, this working group aims to define the scope of this alliance and provide clear distinction with WSSSPE. The group also seeks to understand the incentives for members of this alliance and identify its key activities.
It is currently seeking feedback on potential member organizations, as well as the aims and scope of this alliance.

Currently, point-to-point collaboration exists between organizations, but this inadvertently results in competition or redundancy within the sustainable software community. An alliance of software sustainability organizations would ease inter-organization collaboration and the promotion of software sustainability. This alliance would also improve the pooling of competencies and the sharing of expertise. Furthermore, with the international scope of this alliance, it could support an organization who wants to hold an event in a country where another organization exists.

If interested, visit \url{http://softwaresustainability.org/} or email Neil Chue Hong (<N.ChueHong@software.ac.uk>) and Jean Salac (<jeansalac@virginia.edu>)

\input{wg_prototyping}
\input{wg_codemeta}
\input{wg_best_practices_developing}
\input{wg_social}
\input{wg_best_practices_undergrads}
\input{wg_metrics}
\input{wg_access}
\input{wg_soft_eng}
\input{wg_open_research_index}
\input{wg_letters}
